Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-11 theory.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}. The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}. The quark is absorbed by the nucleon with fraction $x-\xi$. Right: The Bethe-Heitler process which has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

Leptoproduction of real photons \blue{($ep\rightarrow ep\gamma$)} can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
emission of a real photon by a quark from the nucleon\blue{,} and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
emission of a Bremsstrahlung photon by the lepton. 
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment, but the
scattering amplitudes of the two processes interfere and the large BH amplitude
amplifies the contribution of the DVCS amplitude to the interference term. 
It is through the study of this interference term at H{\sc ermes} that
useful information for the constraint of certain GPDs can be obtained.

@@

This paper provides a set of results analogous to those reported in
Ref.~\cite{Air09}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
The results in this paper do not make use of any of the information from the
upgraded detector equipment \blue{(i.e. uses a missing-mass technique for event selection)}, but represent the largest DVCS data set that will
be published by H{\sc ermes}. For more details on the physics implications and general experimental technique,
the reader is referred to Ref.~\cite{Air09}.

There are two sets of asymmetries that are measured at H{\sc
ermes} with an unpolarised target and a polarised electron or positron beam:
beam-helicity asymmetries and beam-charge asymmetries. It is possible to
disentangle the DVCS and interference contributions to the beam-helicity
asymmetry due to the beam-charge dependence of the interference term, so that
this paper, as Ref.~\cite{Air09}, presents results on the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}

>>>>

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
which an electron/positron \blue{($e,e^\prime$)} interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}. The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}. The quark is absorbed by the nucleon with fraction $x-\xi$. Right: The Bethe-Heitler process which has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

Leptoproduction of real photons \blue{($e\,p\,\rightarrow\,e\,p\,\gamma$)} can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
emission of a real photon by a quark from the nucleon\blue{,} and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
emission of a Bremsstrahlung photon by the lepton. 
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment, but the
scattering amplitudes of the two processes interfere and the large BH amplitude
amplifies the contribution of the DVCS amplitude to the interference term. 
It is through the study of this interference term at H{\sc ermes} that
useful information for the constraint of certain GPDs can be obtained.

@@

This paper provides a set of results analogous to those reported in
Ref.~\cite{Air09}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
The results in this paper do not make use of any of the information from the
upgraded detector equipment \blue{(i.e. a missing-mass technique for event selection is used)}, but represent the largest DVCS data set that will
be published by H{\sc ermes}.

There are two sets of asymmetries that are measured at H{\sc
ermes} with an unpolarised target and a polarised electron or positron beam:
beam-helicity asymmetries and beam-charge asymmetries. It is possible to
disentangle the DVCS and interference contributions to the beam-helicity
asymmetry due to the beam-charge dependence of the interference term, so that
this paper \blue{(like} Ref.~\cite{Air09}\blue{)}, presents results on the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}
